An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-03-26 poly-embed-journal/poly-embed-journal.tex
todo

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{ TODO Items 01 Mar 2021
	\begin{itemize}
		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
		\item \sout{Flesh out and expand on Ordered Partition Example}
		\item add paragraph of discussion on the requirements of polyhedral losses
		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
		\begin{itemize}
		\item \sout{for now, move everything up except PDs}
		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks)
		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy
		\end{itemize}
		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
\end{itemize}
TODO Items summer 2020
	\begin{itemize}
		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
		\item Replace Proposition 2 with Lemma 7?
		\item Theorem 2: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
	\end{itemize}}

>>>>

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{ TODO Items 01 Mar 2021
	\begin{itemize}
		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
		\item \sout{Flesh out and expand on Ordered Partition Example}
		\item add paragraph of discussion on the requirements of polyhedral losses
		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
		\begin{itemize}
		\item \sout{for now, move everything up except PDs}
		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
		\end{itemize}
		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
\end{itemize}
TODO Items summer 2020
	\begin{itemize}
		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
		\item Replace Proposition 2 with Lemma 7?
		\item Theorem 2: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
	\end{itemize}}
